Source Code Volatility Metric

### 2020-04-17 paper/article.tex
cite

\citep{biazzini2014} introduced a number of metrics to analyze
Git history (specifically related to GitHub), such as unique-count, unique-ratio,
VIP-count, VIP-ratio, scattered-count, pervasive-count and a few others. Some
of the metrics are supposed to be calculated for a repository together with
its forks, while others may be calculated for a single repository history.

>>>>

\citet{biazzini2014} introduced a number of metrics to analyze
Git history (specifically related to GitHub), such as unique-count, unique-ratio,
VIP-count, VIP-ratio, scattered-count, pervasive-count and a few others. Some
of the metrics are supposed to be calculated for a repository together with
its forks, while others may be calculated for a single repository history.

\citet{batista2018} provided a detailed analysis of existing metrics
and introduced a new one to measure, by looking at Git/GitHub project
commit history, how ``close'' developers stay to each other and form
pairs.
